Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
paper nearly final?

Therefore, we optimized $F_C$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le M\right\}$
of $M$ individuals (Genotypes) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=1ex, leftmargin=0pt]
 \item[Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 50 samples (and adaptively more if the
     $(F_i)_{1\le i\le N}$ are spaced closely, to at most 100).
 \item[Selection] We choose $50\%$ of the most successful members of $G_t$ as survivors.
     With a small chance, a weaker generator can survive, in order to keep the gene pool more diverse.
\item[Reproduction] We then replace the $(1-p)|G_t|$ elements that did not make
    it into the next generation by either \emph{mutating} or \emph{recombining} the 
    survivors and get $\mathcal{G}_{t+1}$. This means we either change
    a single parameter randomly or take two individuals and randomly choose
    for each parameter from which parent to take the value.   
\end{description}

>>>>

Therefore, we optimized $F_C$ using a genetic algorithm, which is inherently
capable of coping with the stochastic fitness function. In each iteration
of the algorithm, a generation $\mathcal{G}_t = \left\{ G_i~|~1\le i\le M\right\}$
of $M$ individuals (genotypes) is converted into a new one, $\mathcal{G}_{t+1}$,
according to the following scheme:
\begin{description}[itemsep=0ex, leftmargin=0pt, format=\normalfont]
 \item[1. Evaluation] The fitness $F_i = F_C(G_i)$ of each individual is
     measured using at least 50 samples (and adaptively more if the
     $(F_i)_{1\le i\le N}$ are spaced closely, to at most 100).
 \item[2. Selection] We choose $50\%$ of the most successful members of $G_t$ as survivors.
     With a small chance, a weaker generator can survive, in order to keep the gene pool more diverse.
\item[3. Reproduction] We then replace the $(1-p)|G_t|$ elements that did not make
    it into the next generation by either \emph{mutating} or \emph{recombining} the 
    survivors and get $\mathcal{G}_{t+1}$. This means we either change
    a single parameter randomly or take two individuals and randomly choose
    for each parameter from which parent to take the value.   
\end{description}
